Metadata collation

### 2023-09-25 metadata/parametadata_control.Rmd
Saving metadata timepoints separately

all_filedata <- samp_filedata %>%
  bind_rows(other_filedata) %>%
  left_join(station_samp_map)
```

@@

```{r}
mzml_timestamps <- grabMSdata(all_filedata$filepath, grab_what = "metadata") %>%
  pluck("metadata") %>%
  select(filename, timestamp)
parametadata <- left_join(all_filedata, mzml_timestamps)
```

>>>>

all_filedata <- samp_filedata %>%
  bind_rows(other_filedata) %>%
  left_join(station_samp_map) %>%
  distinct()
```

@@

```{r}
if(!file.exists("metadata/raw_data/mzml_timestamps.csv")){
  mzml_timestamps <- grabMSdata(all_filedata$filepath, grab_what = "metadata") %>%
    pluck("metadata") %>%
    select(filename, timestamp)
  write_csv(mzml_timestamps, "metadata/raw_data/mzml_timestamps.csv")
}
mzml_timestamps <- read_csv("metadata/raw_data/mzml_timestamps.csv")
parametadata <- left_join(all_filedata, mzml_timestamps)
```
